%----------------------------------------------------------------------------------------
%	Conclusion
%----------------------------------------------------------------------------------------

\chapter{Conclusion}

The development of digital scales and accompanying applications for weighing dogs at the SPCA presents a solution that streamlines the weighing process, improves efficiency, and enhances the well-being of the animals. The project aligns with the SPCA's core values and considerations, incorporating data privacy laws, sustainability practices, and Te Ao Māori principles. The automated weight-taking process, accurate measurements, and automatic data storage eliminate the need for manual recording and minimise stress on the animals. The mobile and web applications provide additional data analysis, communication, and export features, empowering the SPCA staff to work more efficiently. The implementation plan includes stakeholder consultation, prototype modifications, mass testing, compliance certifications, and trials. The report also highlights the importance of societal considerations, sustainability, Te Tiriti o Waitangi principles, and legal and privacy requirements. By addressing these aspects, the project ensures a user-friendly, culturally sensitive, and environmentally conscious solution for the SPCA and its stakeholders. It will take roughly three to four months to test scale prototypes, certify them, and create 60 scales. There is a hardware cost of \$2800 for components, PCB, and assembly. An additional \$700 is estimated to be required for the scale's RoHS certification. As such, the total cost of the project is estimated to be \$3500. The ongoing cost of the software is \$130 per month. Steps have been recommended for the project team to complete after the prototype, where the next step is gaining feedback from the SPCA.

\chapter{}
\section{Bibliography}

“SPCA in New Zealand - SPCA New Zealand,” www.spca.nz. https://www.spca.nz/about/spca-in-new-zealand

“RoHS Compliance Steps to Certification,” www.rohsguide.com. https://www.rohsguide.com/rohs-certification.htm

“WEEE Compliance Regulations,” www.rohsguide.com. https://www.rohsguide.com/rohs-weee.htm

P. Standards Australia/Standards New Zealand, "AS/NZS 5377:2013: Collection, storage, transport and treatment of end-of-life electrical and electronic equipment," Standards Australia/Standards New Zealand, Sydney, NSW/Wellington, New Zealand, 2013.

“Prototype PCB - Online PCB Quote - Full feature custom PCB prototype service at low cost - PCBWay,” www.pcbway.com. https://www.pcbway.com/orderonline.aspx

“SMT PCB Assembly - Online PCB Quote - Full feature custom PCB prototype service at low cost - PCBWay,” www.pcbway.com. https://www.pcbway.com/quotesmt.aspx

“DigiKey Electronics Home,” Digi-Key Electronics. https://www.digikey.co.nz/

\section{References}

[1] “Why use HTTPS?,” Cloudflare. https://www.cloudflare.com/learning/ssl/why-use-https/ (accessed Jun. 01, 2023).

[2] “Appropriate Uses For SQLite,” www.sqlite.org. https://www.sqlite.org/whentouse.html\#:~:text=An\%20SQLite\newline\%20database\%20is\%20limited (accessed Jun. 01, 2023).