%----------------------------------------------------------------------------------------
%	Executive Summary
%----------------------------------------------------------------------------------------

\chapter{Executive Summary}

The SPCA cares for many animals. As part of their care, animals must regularly be weighed as an indicator of their health. Our product will help the SPCA manage the weight of their animals more efficiently and effectively by weighing animals and recording the weights automatically, focusing on dogs between 5 - 25 kgs. We will ensure that the weights are recorded quickly and accurately with our custom-built scale to record dogs weight electronically, and display it through mobile and web front ends and a seven segment LED display. This will be achieved through a combination of hardware systems and software designs. The hardware section will sense a weight applied to the scale and send an electrical signal to a microcontroller. Embedded software on the microcontroller will process the weight measurement and display it on the LED display and send the data using WiFi to the software on a staff member’s phone or computer. The software will record this weight and keep track of a dog’s biometric history. This will help SPCA staff members to better organise this data. The intuitive interface of the software will make it easy for staff to use, and we aim for our product to have a steep learning curve to ensure that the system can be operated with ease, speed, and minimal obstacles. 
Our application is designed with a number of societal factors in mind that are relevant in New Zealand. Firstly, we will design the system to fulfil our treaty obligations to make the system usable by different cultures including Māori. For example, In Te Ao Māori, data is taonga and we must recognize tangata whenua as kaitiaki of their data. To fulfil this obligation we need processes in place to allow any user to maintain full control over their data including access, management, deletion. In terms of legal and privacy, collecting data, holding data, and using and disclosing data are fully considered and implemented to further strengthen the link of treaty obligations and the privacy act. Multiple levels of security and access are used in our application to protect the confidentiality and integrity of the system. To ensure sustainability, we will also design our circuit in a way that uses the least amount of materials and dispose of them correctly after use. Other than this, we can choose to use components that comply with the RoHS restrictions and are less harmful to the environment.
Overall, our scale is a product that has the potential to benefit the SPCA by making it easier  for staff and volunteers to regularly measure weights of animals, as well as organising that data. 
